---
title: "CIA-3"
author: "Nidhi Jaidev"
date: "2025-04-13"
output: html_document
---
---
title: "Chi-Squared Test"
author: "Nidhi Jaidev"
date: "2025-04-07"
output: html_document
---



```{r setup, message=FALSE, warning=FALSE}
# Load necessary libraries
# Load libraries
library(dplyr)
library(ggplot2)
library(lubridate)
library(knitr)


##Social Concern: swiss Data

```{r load_data}

# Load dataset
data(swiss)

# Convert row names to a column
swiss$Province <- rownames(swiss)
```
# Bar chart for Education

```{r}
ggplot(swiss, aes(x = reorder(Province, -Education), y = Education)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Education Level by Province", x = "Province", y = "Education (%)")

```

#Environmental Concern: CO2 Dataset

```{r load_data}

#Load dataset
data(CO2)

``` 
  
# Line chart of CO2 uptake

```{r}
ggplot(CO2, aes(x = conc, y = uptake, color = Type)) +
  geom_line(aes(group = interaction(Plant, Type)), alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  labs(title = "CO2 Uptake by Concentration", x = "CO2 Concentration", y = "Uptake Rate")

```

#Societal Concern: gapminder Dataset

# Install and load gapminder
install.packages("gapminder")
library(gapminder)
library(dplyr)


```{r load_data}

# Filter data for 2007
data_2007 <- subset(gapminder, year == 2007)


```
# Scatter plot

```{r}
plot(data_2007$gdpPercap, data_2007$lifeExp,
     log = "x",
     col = "blue",
     pch = 16,
     main = "Life Expectancy vs GDP (2007)",
     xlab = "GDP per Capita (log scale)",
     ylab = "Life Expectancy")
```
